% LaTeX file for resume
% This file uses the resume document style (res.sty)
\documentclass[margin]{res}
%%\usepackage{mdwlist}
%%\usepackage{enumitem}
\setlength{\topmargin}{-0.5in}
\setlength{\textheight}{10.5in}

\textwidth=5.7in % increase textwidth to get
         % smaller right margin
\sectionwidth=1.0in


\begin{document}

\name{Dr. David Andrews}

\address{david.andrews112@gmail.com \ \ \ (949) 633-0588}

\begin{resume}
%\bigskip

\section{OBJECTIVE}
A challenging and dynamic engineering leadership position with an innovative, motivated team.


\section{SKILLS}
\begin{list}{}{\leftmargin=0em \topsep=0pt \partopsep=0pt \parsep=2.5pt}
  \item Leading, growing and advancing large engineering teams whose work comes together to produce a global service 
  \item Architecting, building and operationalizing distributed systems at scale (~18,000 server global CDN).
  \item Proficient in C++ and C.
  \item Working knowledge of computer security, Linux, Windows internals and x86\_64.
  \item Working knowledge of open-source tool chains, internetworking,
    Bash, Python, Lua, Golang, various NoSQL and relational databases, \LaTeX{} documentation.
  \item Previously worked with Perl, PHP, HTML, Javascript.
  \item Architectural understanding of cloud and k8s concepts and systems.
\end{list}

%{\bf Programming:} C++ (preferred), C, PHP, PERL, Javascript, Bash, Python (minimal). \\
%{\bf Environments:} Linux/Unix (preferred), Windows. \\
%{\bf Protocols:} TCP/UDP/IP, HTTP (1.1, 2, 3), DNS.


%\section{COMMUNICATION SKILLS}
%Directed a team of 8 developers in consistent scheduled releases and deployments. \\
%3 years lecturing and tutoring both domestic and international students. \\
%Uncontested PhD candidature confirmation.


\section{EXPERIENCE}
\noindent

{\bf Vice President, Engineering}\\
Edgio Inc (formerly Yahoo EdgeCast), CA {\em (2022-present)}
%\begin{list}{\labelitemi}{\leftmargin=1em}
\begin{list}{\labelitemi}{\leftmargin=1.5em \topsep=5pt \partopsep=0pt \parsep=2.5pt}
  \item Led both Infrastructure and Engineering teams through the transition from Verizon to Edgio.
  \item Designed and contributed to real-time global configuration system (~5 second global propagation)
  \item Defined and implemented new change management processes and procedures
  \item Primary technical subject matter expert for PCI DSS, SOC2, ISO27K1 certifications
  \item High Priority Incident 'quarterback' (incident commander) (1 of 2)
  \item Designed and contributed to obseravability and operational improvements for core services
  \item Key leader in right-sizing initiatives across engineering and infrastructure
\end{list}

{\bf Sr Director, Engineering and Chief Architect,} previously Content Delivery Network Architect and Evangelist.\\
Yahoo EdgeCast (formerly Verizon Digital Media Services), Los Angeles, CA {\em (2016-2022)}
%\begin{list}{\labelitemi}{\leftmargin=1em}
\begin{list}{\labelitemi}{\leftmargin=1.5em \topsep=5pt \partopsep=0pt \parsep=2.5pt}
  \item Engineering responsibility for 2/3rds of the core Content Delivery Network (CDN) team, covering core platforms, SRE, traffic management.
  \item Founding member of the Oath Inc./Yahoo Senior Tech Council
  \item Key driver for product decisions and architecture (analytics, configuration management, customer dev tooling: SDK, CLI, APIs, IaC).
  %\item Coordination and primary stakeholder for engagement with central support teams.
  \item Providing architectural and operational guidance to both CDN and video streaming engineering and operational teams.
  \item Architecting and leveraging scaled bare-metal distributed systems, and cloud-based systems cohesively.
  \item Responsible for architectural and change management review of all engineering projects and deployments.
  \item Founding member of Verizon open source committee.  Verizon github owner.
  \item Community participation: conference keynotes and panels, technical blogs, meetup hosting.
\end{list}

{\bf Security Core Team Lead,} previously Principal Software Engineer.\\
Verizon Digital Media Services (formerly EdgeCast), Los Angeles, CA {\em (2012-2016)}
%\begin{list}{\labelitemi}{\leftmargin=1em}
\begin{list}{\labelitemi}{\leftmargin=1.5em \topsep=5pt \partopsep=0pt \parsep=2.5pt}
  \item Lead team developing Web Application Firewall and Layer 7
    Anti-DDoS products.
  \item Key contributor in deploying a PCI-compliant network for e-commerce customers.
  \item Primary forensic investigator of internal security incidents.
    FBI technical liason.
  %%\item Responsible for secure coding practices training company-wide.
  \item Owner of modifications to the core web-server to support PCI
    compliance.
\end{list}

{\bf Director of Development,} previously Sr. Software Architect. \\
CounterTack (formerly NeuralIQ) Inc., Santa Monica, CA {\em (2006-2012)}
%\begin{list}{\labelitemi}{\leftmargin=1em}
\begin{list}{\labelitemi}{\leftmargin=1.5em \topsep=5pt \partopsep=0pt \parsep=2.5pt}
  %\item Heavy emphasis on workflow iteration to improve developer
  %  efficiency.
  \item Project owner of a hypervisor-based OS introspection module
    (Patented). Runtime configurable to collect function
    calls (kernel, syscall or userland) and packets on 100\%
    unmodified virtual machines.
  \item Project owner of a real-time OS analysis engine supported by a
    custom graph-based simulation database (Patented).
  %% \item Project owner of a high-performance multi-threaded daemon
  %%   responsible for serving both atomic and persistent
  %%   publish/subscribe requests for analysis data.
  %% \item Project owner of a dynamically-sizeable buffering library
  %%   providing in-memory, and file-backed buffers for streaming
  %%   data between threads or processes.
  %% \item Project owner of a file caching library designed for
  %%   high-performance random access (\string~8x faster than {\em
  %%     lseek() + read()}) and sequential writing (\string~2x faster
  %%   than {\em write()}).
  %%\item Responsible for new developer hiring, training.  Trained 15+
  %%  new employees.
\end{list}

%% {\bf Software Engineer.} \\
%% Defence Science Technology Organisation, Vic, Australia {\em (2002-2005)}
%% \begin{list}{\labelitemi}{\leftmargin=1.5em \topsep=5pt \partopsep=0pt \parsep=2.5pt}
%%   \item Developed interoperability middleware for distributed simulations.
%%   \item Developed an optimizing scheduler for Australian Naval activities.
%% \end{list}

%% {\bf IT Consultant} \\
%% R G Technologies, Victoria, Australia 2002-Present \\
%% \begin{itemize}
%%   \item Support of small Linux-based network (3 sites, 6 servers, 100+ workstations).
%%   \item Adaptation and customisation of open-source web groupware.
%% \end{itemize}

%{\bf Lecturer / Tutor.} \\
%University of Ballarat, Vic, Australia {\em (2000-2004)}  \\
%\begin{itemize}
%  \item Lectured: Masters course on .NET Programming;
%  \item Tutored: Undergraduate courses on Network Operating Systems, C, C++ and Java Programming.
%\end{itemize}

%{\bf Part-Time Website Developer} \\
%Self-Employed, 1996-Present \\
%\begin{itemize}

%  \item Flash website creation. {\it Example at http://www.rgt.com.au/dave/newgen2.html}
%\end{itemize}

\section{PATENTS}
 Low Latency Video Streaming Via A Distributed Key-Value Store 20190394512 A1
 Optimized Message Flooding Across Nodes Of A Distributed Platform: 20190149460 A1
 Rapid Configuration Propagation In A Distributed Multi-Tenant Platform: 20190081862 A1
 Distributed Rate Limiting: 20170180414 A1
 Unobtrusive And Dynamic DDoS Mitigation: 20160344765 A1
 Real-Time Reconfigurable Web Application Firewall For A Distributed Platform: 20160182454 A1
 System And Method For Sampling Forensic Data Of Unauthorized Activities Using Executability States: 20110321165 A1
 System And Method For Identifying Unauthorized Activities On A Computer System Using A Data Structure Model: 20110321166 A1
\section{EDUCATION}

{\bf Doctorate of Philosophy.} \\
University of Ballarat, Vic, Australia {\em (2002-2006)}
\begin{list}{\labelitemi}{\leftmargin=1.5em \topsep=5pt \partopsep=0pt \parsep=2.5pt}
  \item Thesis on computer security via abstracted program behaviour modelling.
  %\item https://researchonline.federation.edu.au/vital/access/manager/Repository/vital:996
\end{list}

{\bf Bachelor of Computing (Hons).} \\
University of Ballarat, Vic, Australia {\em (1999-2002)}
\begin{list}{\labelitemi}{\leftmargin=1.5em \topsep=5pt \partopsep=0pt \parsep=2.5pt}
  \item 6.87/7 GPA and 1st Class Honours, thesis on distributed simulation security.
  \item Heavy focus on programming (C and C++), lighter focus on networking.
%\item Completed networking track: TCP/IP-focus.
\end{list}


\section{OPEN SOURCE}
https://github.com/thehelix112

%\section{Distinctions}
%Golden Key International Honours Society chapter's executive committee member. \\
%High Distinction average undergraduate grade. \\
%Secondary school national ranking of {\bf 97.70} out of 99.95 (top 2.25 percentile nationally). \\


%{\bf Internet Service Provider Helpdesk,} The Friendly Giant, 2000-2001 \\
%\begin{itemize}  \itemsep -2pt
%\item
%\end{itemize}

%{\bf Gymanstics Coach,} Ballarat YMCA, 1994-2000 \\
%\begin{itemize}  \itemsep -2pt
%\item
%\end{itemize}


%\section{Hobbies \& Interests}
%Historic Car Racing, Skating, Gymnastics, Tae Kwon Do, Boxing.



\end{resume}
\end{document}
